Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix subject/verb agreement. A timer...it refers.

Running a Raft cluster in a browser context can lead to some level of
timer instability. The JavaScript execution context is a fully event
driven environment with a single thread of execution for a given
JavaScript context. JavaScript code is run when browser (or Node.js)
events trigger JavaScript code that is registered to that event. In
order to implement logic that runs periodically, JavaScript code is
registered as a callback timer using the setTimer, setInterval or
requestAnimationFrame APIs. However, none of these mechanisms is
a precise timer. When a timer fires, the callback code they refer to
is added to the JavaScript execution queue and events on the queue are
processed in the order they arrive. This means callbacks may be
delayed by other code that is already running or queued first
\cite{resig2013secrets}.

>>>>

Running a Raft cluster in a browser context can lead to some level of
timer instability. The JavaScript execution context is a fully event
driven environment with a single thread of execution for a given
JavaScript context. JavaScript code is run when browser (or Node.js)
events trigger JavaScript code that is registered to that event. In
order to implement logic that runs periodically, JavaScript code is
registered as a callback timer using the setTimer, setInterval or
requestAnimationFrame APIs. However, none of these mechanisms is
a precise timer. When a timer fires, the callback code it refers to
is added to the JavaScript execution queue and events on the queue are
processed in the order they arrive. This means callbacks may be
delayed by other code that is already running or queued first
\cite{resig2013secrets}.
